%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Twenty Seconds Resume/CV
% LaTeX Template
% Version 1.0 (14/7/16)
%
% Original author:
% Carmine Spagnuolo (cspagnuolo@unisa.it) with major modifications by 
% Vel (vel@LaTeXTemplates.com) and Harsh (harsh.gadgil@gmail.com)
%
% License:
% The MIT License (see included LICENSE file)
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[letterpaper]{twentysecondcv} % a4paper for A4

% Command for printing skill overview bubbles
% \newcommand\skills{ 
% ~
% 	\smartdiagram[bubble diagram]{
%         \textbf{Data}\\\textbf{Engineering},
%         \textbf{Full Stack}\\\textbf{Dev},
%         \textbf{~~~~~~~~OOP~~~~~~~~~},
%         \textbf{~~~~~~Machine~~~~~~}\\\textbf{~~Learning~~},
%         \textbf{~~~~~DevOps~~~~~}
%     }
% }

% Programming skill bars

\programming{ {Assembly $\textbullet$ VHDL / 2},
{HTML $\textbullet$ PHP $\textbullet$ SQL  / 2.5}, 
{C++ $\textbullet$  \large \LaTeX / 4}, 
{C  $\textbullet$ Python  $\textbullet$ Java / 4.5}}

% Projects text

\education{
\textbf{B.S., Computer Science} (GPA: 3.5) \\
\textbf{Minor: Mathematics} \\
University of Nebraska-Lincoln \\
2017 - 2021 | Nebraska, America \\
Courses: \\
\textbf{CSCE 322:} Programming lang Concepts \\
\textbf{CSCE 361:} Software Engineering \\
\textbf{CSCE 351:} Operating Sys Kernel \\
\textbf{MATH 314:} Linear Algebra \\

\textbf{High School Diploma} (GPA: 3.94) \\
Lincoln Christian Highschool\\
2016 - 2017 | Nebraska, America
}

%----------------------------------------------------------------------------------------
%	 PERSONAL INFORMATION
%----------------------------------------------------------------------------------------
% If you don't need one or more of the below, just remove the content leaving the command, e.g. \cvnumberphone{}

\cvname{Huy Vuong} % Your name
\cvjobtitle{B.S., Computer Science} % Job
% title/career

\cvlinkedin{/in/huynvuong/}
\cvgithub{HuyNVuong}
\cvnumberphone{(415) 818 7070} % Phone number
\cvsite{cse.unl.edu/ \textasciitilde hvuong/} % Personal website
\cvmail{huynguyenvuong99@gmail.com} % Email address

%----------------------------------------------------------------------------------------

\begin{document}

\makeprofile % Print the sidebar
 \section{Summary}
    I am a motivated Computer Science students who is actively looking for internship
%----------------------------------------------------------------------------------------
%	 EXPERIENCE
%----------------------------------------------------------------------------------------

\section{Experience}

\begin{twenty} % Environment for a list with descriptions
\twentyitem
    	{Aug 2018 -}
		{Present}
        {Undergraduate Teaching Assistant}
        {}
        {}
        {\begin{itemize}
        \item Taught Computer Science I: Foundation of Computer Science and currently teaching Computer Science II: Object-Oriented Programming and Computer Science III: Data Structure and Algorithms.
        \item Grading, Supervising and helping in lab session.
        \item Holding office hours to help students with course related problems
        \item Helping students familiarize with several different programming languages, debugging as well as classifying different types of errors.
        \item Guiding students to design an efficient and well organized project.
        \item Introduce students to Algorithm Analysis and Big-O notation
        \item Presenting students at deriving different algorithms as well as data structures 
        \end{itemize}}
        \\
	\twentyitem
    	{May 2018 -}
		{Sep 2018}
        {Student Worker - Information Technology Service}
        {}
        {}
        {
        {\begin{itemize}
        \item Provided general university information and technical support
        \item Troubleshooted university accounts and technical related problems
        \item Directed switchboards call around university
    \end{itemize}}
        }
    
        
	%\twentyitem{<dates>}{<title>}{<location>}{<description>}
\end{twenty}

%----------------------------------------------------------------------------------------
%	 INVOLVEMENTS
%----------------------------------------------------------------------------------------

\section{Involvements}
\begin{twenty}
	\twentyitem
    	{Dec 2018}
		{}
        {Advent of Code - 2018}
        {\href{https://github.com/HuyNVuong/AdventOfCode}{Link to GitHub}}
        {}
        {
        25 days of programming, with each day present a new challenges
        {\begin{itemize}
        \item Practiced my algorithm as well as problem solving skills.
        \item Manipulated directly to test cases to get the correct answer.
        \item Learned many features of Python to help creating test cases as well as solving them faster and more convinient.
		\end{itemize}}
        }
    \\
    \twentyitem
    	{Oct 2018}
		{}
        {ACM ICPC Local - 2018}
        {\href{https://github.com/HuyNVuong/ACM-2018}{Link to GitHub}}
        {}
        {
        Local North America ACM contest
        {\begin{itemize}
        \item Team up with other 2 members to write algorithms to solve different type of problems in 5 hours.
		\end{itemize}}
        }
    \\
    \twentyitem
    	{Aug 2018}
		{- Present}
        {CSE Ambassador}
        {}
        {}
        {
        {\begin{itemize}
        \item Back-end programmer in Dev team .
        \item Phase developer for Coding and Coffee.
		\end{itemize}}
        }
\end{twenty}

%----------------------------------------------------------------------------------------
%	 PROJECTS
%----------------------------------------------------------------------------------------
\section{Projects}
\begin{twenty}
	\twentyitem
    	{Dec 2018 - }
		{Present}
        {Simple video game}
        {} % Link to GitHub goes here
        {}
        {
       	Building different type of simple classic game from scratch to understand how's game are built as well as to improve my programming skills
       	
       	\textbf{Game developed:}
        {\begin{itemize}
        \item Snake
        \item Tetris
		\end{itemize}}
        }
    \\
    \twentyitem
    	{Mar 2018}
		{}
        {Nebraska Livestock Visualization}
        {\href{https://github.com/HuyNVuong/Nebraska-livestock-Visualisation}{Link to GitHub}} % Link to GitHub goes here
        {}
        {
       	Hackathon hosted by UNL - 24 hours programming contest
       	
       	\textbf{Achivement:}
        {\begin{itemize}
        \item Created dynamic visualization of large amount of datas collected over times
        \item Familiarized with Front and Back end web development.
        \item Familiarized and used with PHP, JavaScript, HTML, CSS, MongoDB
		\end{itemize}}
        }
\end{twenty}

\end{document} 
